\LARGE \bf \pyRobots, a toolkit for robot executive control

### 2014-08-20 paper.tex
First pass on the introduction

A set of software helpers to write high-level robot controllers.

\emph{Not} a middleware: it connects to one or several middleware to actually
perform actions.

The toolkit does not aim at formal verifiability: no contribution in this field.

@@

\begin{itemize}
    \item FSM -> SMACH
    \item agent-based approaches -> ROAR
    \item logic languages -> OpenPRS, CRAM
    \item dedicated control languages -> URBI
    \item similar attempts: teer (co-routine -> cooperative multi-threading)
    \item and the vast majority: ad-hoc scripts
\end{itemize}

>>>>

Orchestrating the activity of a robot is a central issue of robotics: \emph{what
to do when?} Traditionally, in the famous 3-layer architectures~\fixme{ref?},
this function is implemented in the so-called \emph{deliberative layer} where
decisions are made based on perceptions and on the current internal state, and
executed by sending orders to a \emph{functional layer}.

While individual decision-making components (like task planners) are studied in
(relative) isolation since years, the \emph{orchestration} issue, with questions
like \textit{When to start them? Which one should be selected? How to react to a
new situation in a timely manner?} remains difficult to address in a generic
way.

Many approaches have been devised (we review them in the next section) that
include \emph{Finite State Machines} (FSM), domain-specific languages (in
particular, logic languages) or agent-based frameworks.

These tools adopt principled approaches, often with solid theoretical
contributions. However, it seems that none of them gained broad acceptance in
the robotic community, and many of us resort to write ad-hoc scripts, suitable
for a single application/demonstration/experiment and neither reliable nor
extensible.

We hypothesize that the software architecture design that these tools enforce,
combined with their general lack of practicality (unfamiliar language; lack of
bindings for a given robot or middleware; difficulty to install or setup;
non-trivial deployment) explain this low level of acceptance more than any
particular intrinsic weaknesses.

This article introduces our attempt at designing an unobtrusive execution control
toolkit, that aims at addressing the \emph{practicality} issue: it has been
designed and implemented from the bottom-up, starting from actual needs when
running complex robots in largely unpredictable scenarios (typically,
loosely constrained human-robot interactions), and in the real world.

Instead of an \emph{environment} or a \emph{framework}, which would suggest
strong design and development constraints, \pyRobots can be conceived as a set of
powerful software helpers to write parallel, event-based, high-level robot
controllers.

It is written for and in Python, which ensure familiarity, fast development
cycles and broad support for interfacing with existing robots and middlewares.
This must be emphasized: \pyRobots is \emph{not} a middleware. It purposefully
provides no mechanisms to connect to other modules or components. It instead
\emph{uses} one (or several) middleware to actually communicate with the robot
and perform actions.

One the other hand, \pyRobots does not provide formal models or verifiability:
in its current state, it does not attempt to contribute in this field. It
focuses instead on providing unobtrusive tools to control robots in environments
that require carrying out many tasks in parallel, in an unpredictable,
event-based manner.

@@

\begin{itemize}
    \item FSM: SMACH
    \item agent-based approaches: ROAR
    \item logic languages: OpenPRS, CRAM
    \item dedicated control languages: URBI
    \item similar attempts: teer (co-routine: cooperative multi-threading)
    \item and the vast majority: ad-hoc scripts
\end{itemize}
